<small> Supplementary materials for the main submission entitled - <br><br> A new metric for automatic discovery of periodic patterns in time series

### 2021-05-05 paper/paper-supplementary.Rmd
structure update

## Different underlying distributions

@@

```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution. The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
```
## Different number of comparisons

@@

# Normalised distance measure

>>>>

## Underlying distributions

@@

```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution. The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
```
## Number of comparisons

@@
